Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-20 chapters/introduction/introduction.tex
minor change

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs achieve state-of-the-art performances in
many computer vision areas (\todo{citations}). 
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geolocalization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image.

@@

\section{Our Approach}
We divide our approach in two steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions that describe the fitness between the calibration
parameters and the images. Then we dismantle the full geo-calibration
into several partial geo-calibration tasks, each of which provide a
constraint function that could fit into our general model.

\subsection{General Probabilistic Model for Geo-Calibration}
The complete camera geo-calibration includes the detection of camera
geographic location, the pose and the focal length of the camera.  We
design a graphic model to estimate the probability over these
geo-calibration parameters. 
We construct an scoring function to measure the ``fitness'' between
the calibration parameters and the observation of the image. The
scoring function is proportional to the probability distribution of
the camera parameters. We propose a Markov Chain Monte Carlo (MCMC)
sampling approach to approximate the underlying probability
distribution over the full geo-calibration of the camera.
Our model is a general architecture, which can take different
constraints to form the energy function. The details about this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In our general model, the scoring function is defined as a linear
combination of multiple constraint functions. We then develop
these constraint functions to describe different calibration
parameters.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Horizon Line and Vanishing Points:}
  We first estimate camera roll and pitch angles. Assuming the intrinsic
  parameters are known, camera roll and pitch angles can be
  derived from the horizon line position in the image. Detecting horizon
  line is easier because it is tightly related to the content/appearance
  of the scene. In our work, we first create a new method using DNNs to
  give a prior distribution of the horizon line, then assign a
  probability to each by measuring their consistences with vanishing
  points detected using traditional statistic methods. \newline

  \item \textbf{Constraint for Coarse Geographic Locations:}
  In this work, we demonstrate that we can estimate the camera geographic
  location with the input image and its temporal information.
  One of the key to the success of machine learning approaches are the
  large quantity of annotated data. However, fully annotated imagery
  only consists of a tiny part of the image resources available online.
  The idea is to exploit other meta-info that are automatically
  recorded/captured by devices to train the ML models. We demonstrate
  that the camera geometry can be used as weak ground truth for
  supervision problem. By learning the capture time and the geolocation
  of the images, our network is able capture the geo-temporal related
  high-level features. \newline

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  With the rough geographic location, we are able to refine the result
  with overhead images.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. \newline

>>>>

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs have achieved state-of-the-art performances in many computer
vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
information, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from aerial imagery that can be matched to features extracted
from ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geolocalization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.  Horizon line is
important indicator for estimating camera poses.
Work~\cite{workman2016horizon, hold2017perceptual} has been done to to
identify the horizon line using an end-to-end CNN. Workman
\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
neural network that can do 6-DOF camera relocalization, but their
method only limited to specific scenes.

@@

\section{Our Approach}
We divide our approach in two steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions that describe the fitness between the calibration
parameters and the images. Under this guidance we dismantle the full
geo-calibration into several partial geo-calibration tasks, each of
which provides a constraint function that could fit into our general
model.

\subsection{General Probabilistic Model for Geo-Calibration}
The complete camera geo-calibration includes the detection of camera
geographic location, the pose and the focal length of the camera.  We
design a general model to estimate the probability over these
geo-calibration parameters: First, we construct a scoring function to
measure the ``fitness'' between the calibration parameters and the
observation of the image. The scoring function is proportional to the
probability distribution of the camera parameters. Then we propose a
Markov Chain Monte Carlo (MCMC) sampling approach to approximate the
underlying probability distribution over the full geo-calibration of
the camera. 
Our model is a general architecture, which can take
different constraints to form the energy function. The details about
this model can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In our general model, the scoring function is defined as a linear
combination of multiple constraint functions.
In the rest of the work, We focus on developing good constraint
functions for different set of calibration parameters.

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Horizon Line and Vanishing Points:}
  We first estimate camera roll and pitch angles. Assuming the intrinsic
  parameters are known, camera roll and pitch angles can be
  derived from the horizon line position in the image. Detecting horizon
  line is easier because it is tightly related to the content/appearance
  of the scene. In our work, we create a new method using a CNN to
  estimate the prior distribution of the horizon line. We then assign
  a probability to each horizon line by measuring their consistences
  with vanishing points detected using traditional statistic methods.
  We present the algorithm details in \chapref{fasthorizon}.
  \newline

  \item \textbf{Constraint for Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the camera geographic
  location with the input image.
  We provide two approaches to obtain the probability distribution over the camera
  geographic location. Most straightforwardly, our network output
  categorical distribution over world into a $N \times M$ bins. Better
  results can be obtained with temporal inputs (image timestamps). Other
  than that, our algorithm can also compute the probability for any
  geographic location.
  We present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  With the rough geographic location, we are able to refine the result
  with overhead images.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. 
  We present the algorithm details in \chapref{crosstransf}
  \newline
